Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-07-01 optim.tex
update illustration

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, rightrule=.15mm, breakable, opacityback=0, toptitle=1mm, colbacktitle=quarto-callout-note-color!10!white, colback=white, bottomrule=.15mm, arc=.35mm, toprule=.15mm, bottomtitle=1mm, titlerule=0mm, opacitybacktitle=0.6, coltitle=black, title={Algorithm: Jellyfish Optimizer Pseudo Code}, leftrule=.75mm, left=2mm]

@@

The new JSO is integrated with the current implementation of the
projection pursuit guided tour in the \texttt{tourr} package, and can be
further examined using PP optimisation diagnostics in the \texttt{ferrn}
package. Using the JSO is a little different than the current CRS,
because it runs many paths. The recommended approach is to conduct the
optimisation off-line, and then use the guided tour to follow selected
jellyfish. The tools for this are available in the \texttt{tourr}
package, too.

>>>>

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, titlerule=0mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, arc=.35mm, breakable, toptitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, bottomrule=.15mm, colback=white, opacityback=0, left=2mm, toprule=.15mm, opacitybacktitle=0.6, bottomtitle=1mm, colframe=quarto-callout-note-color-frame, rightrule=.15mm]

@@

The new JSO is integrated with the current implementation of the
projection pursuit guided tour in the \texttt{tourr} package, and can be
further examined using PP optimisation diagnostics in the \texttt{ferrn}
package. Using the JSO is a little different than the current CRS,
because it runs many paths. The recommended approach is to conduct the
optimisation off-line, extract the bases of a selected jellyfish, and
then use the planned tour to follow selected jellyfish. The tools for
this are available in the \texttt{tourr} package, too.
